Active Learning: Because Guesswork is Overrated

### 2025-02-03 doc/paper.tex
Add final push with updated paper figure and little addition to method section

A multitude of query strategies are used to compare a single model to an ensemble of models. As a control metric, Random Sampling is used to give a baseline for other query strategies.\\

>>>>

A multitude of uncertainty-based query strategies are used to compare a single model to an ensemble of models. Uncertainty-based methods are chosen because they prioritize samples the models are least confident about, making them an effective approach in active learning. They try to improve model performance with fewer labeled samples by focusing on unclear cases, which are particularly relevant in a setting where labeling is expensive. Additionally, they are computationally straightforward. \\
As a control metric, Random Sampling is used to give a baseline for other query strategies. \\
